%I should probably thank someone because I'm not a degenerate.
I think anyone who has been through grad school knows that one lone grad student a dissertation does not make. There have been many people along the way who helped set me on this path, guided me through it, and  supported me throughout. I'd like to start this thesis properly by gushing about the awesomeness of my advisor, Liz Hays. Liz has been infinitely supportive, patient, and encouraging of me, especially in times of doubt (which are many in grad school). She has been a fount of knowledge and wisdom (both of the academic and non-academic variety), and is ever so deft at nudging me in the right directions while simultaneously allowing me to lead and figure things out on my own. If only a few of these qualities have rubbed off on me, I'd be a better person and scientist for it. I can't imagine going through and getting through this journey without her and I'm proud to be her first grad student. 

I am grateful to Cole Miller for being the head of my thesis committee and co-advisor. Cole's advice is always insightful and his steadfast confidence in my abilities has been invaluable to the completion of this thesis. I'd also like to thank Chris Reynolds, Derek Richardson, and Jordan Goodman for serving on this thesis committee and coming along for the ride.

The \Fermi{} collaboration has been a warm and welcoming lot, and I'm thankful for the opportunity to be a part of their ranks. This thesis would not be what it was without the chance afforded by the collaboration to work with several of its members. Thanks to Marco Ajello and  Alberto Dominguez (who were ever so eager to have me handle the mess of sources in the Galactic plane) for letting me take a leading role on the 2FHL paper. Thanks to Marianne Lemoine-Goumard for inviting me to spend a week working with her in France and commiserating over extended source analysis. 

Goddard has been my home away from home for some time now, and my windowless office would have been way less sunny if not for the Goddard \Fermi{} contingent. Thanks to Jack Hewitt for always having an open door and answering every supernova remnant question I could throw at him. I'm grateful for the Goddard \Fermi{} grad students, Sylvia Zhu, David Green, Jeff Magill, Megan DeCesar, and Judy Racusin (who, I know, is not a grad student) for being there to science with, companionship, impromptu matplotib color scheme discussions, as well as conference high jinks and general tomfoolery. 

I'm thankful to Zeph Landau without whom I would definitely not be in Maryland and to Jack Depalma for turning me on to physics and expounding on the merits of paregoric for teething babies and Procul Harem.

This being my doctoral dissertation, I think I'm afforded one or two overly sappy sentiments, so here they are. I wish my father could be here to see this accomplishment and that he could have seen me be more than a high school screw up. I'm forever indebted to my Grandmother for taking me in and being a parent to me when I had no other. It is truly unfathomable what state my life would be in without her. 

Thanks to my kids,  Elliott and June, who if anything have made this thesis tougher,  but they’re pretty cool none the less. 

Lastly, and most importantly, I'd like to thank my dearest dear of a wife, mother of \sout{dragons} our children, Vanessa. She's pretty darn awesome! She's always ready to lift me up when I'm down, and I'm lucky she threw her lot in with me. Also, I appreciate her lack of a fetching beard. 

