\chapter{Gamma-ray Astronomy }
\label{chap:gamAstr}

\section{Introduction}\label{gamAstr:intro}
\jamie{I might move the emission mechs section into the snr chapter, and move the rest of this section into the introduction, or just call the intro chapter gam Astro}
The story of \gam 's from astrophysical objects is a tale of the most extreme, energetic, and violent environments in our universe. Discovered by Paul Villard studying radiation from radium and named by Ernest Rutherford, who previously uncovered the nature of $\alpha$ and $\beta$ radiation, \gam's are the highest named energy of light 

more historical context 

what is a gamma-ray

why bother studying gamma-rays

probe of extreme environments

snrs as source of Galactic cosmic rays, and thus as drivers of Galactic evolution

\section{\gam~Emission Mechanisms }\label{gamAstr:Emiss}

\cite{Sturner97}
\cite{Gaisser98}
Gamma-rays as a probe of cosmic rays and cosmic acceleration processes

PP collisions if one is at rest give two about 67\mev{} photons
protons are tougher because the mass is higher, interaction cross section is smaller, higher energy B field requited to observe proton synchrotron and we expect it to be weaker.  and we don't typically detect radiation from protons, EXCEPT PP and this leads to gammas

gamma-ray astronomy as  a proxy for studying cosmic rays and acceleration/diffusion processes. How much to get into CR. 

Cosmic particle accelerators and \gam's
accelerator plus target often 


What's a CR, quick,  general CR properties that are relevant to SNRs

why use gamma's  to study CR

gamma-ray production mechanisms

myriad of gamma-ray generating mechanisms operate at this energy, so it's sometimes the only range that we can observe this emission in:

-Synch,
-Bremss,
-IC,
-pi0,

\section{Sources of \gam's}\label{gamAstr:Sources}
Maybe don't need this? The reason to is to say SNRs early on. Would I mention other sources to be complete?

\section{\gam{} Detection}\label{gamAstr:Detect}
Maybe this should just be a quick history of \gam{} telescopes leading up to fermi?
Quick rehash of method of detecting \gam's? Or is this just about previous \gam ~detectors and the state of the \gam~sky pre-Fermi?  mention telescopes up to EGRET, bit of detail on EGRET and what the pre-Fermi \gam~sky looked like, in particular in the context of SNRs, PWN, Galactic plane

gamma-ray telescopes leads into the LAT, Egret was  predecessor , what it did and what were some relevant unanswered questions regarding supernova remnants 


One of the primary goals of fermi was to identify these sources and the site of CR acceleration. But also to uniquely open this high energy window that where no other telescopes really operated
Brief history of radio detection of SNRs. detection at other wavelengths. what we see at \g-rays?

Motivation for why to study them
\citep{Sturner95}
\citep{Esposito96}

\section{Scratch}

Altho' many miles from bomb zero, Dr. Bruce Banner is bathed in the full force of the mysterious Gamma Rays!

thermal means follows maxwellian (maxwell-Boltzman) distribution