\chapter{Overview}
\label{chap:intro}

\begin{quote}
	``Maybe I'll have a super relevant quote here!'' 
	\begin{center}---by some awesome human, from \it{Some book} \end{center}
\end{quote}
%\begin{figure*}
%  \centering
%  \epsscale{1}
  % Jamie commented this out for now
 % \plotone{figures/filename-with-no-extension}
%  \caption[Short Caption]{Long caption}
%  \label{fig:somelabel}
%\end{figure*}

\section{Goooo $\gamma$-rays go!}
\jamie{Maybe I should just move the gamma-ray astro, LAT, and SNR chapters here and have them all be  sections in the intro. Or maybe, This section is a super short overview of the entire thesis, next section is all the bkg.}
In this thesis we...or should I start with the extreme environs line?

Overview of the entire thesis, why gamma-rays, why the \lat, why \snr and \pwn and extended sources.

Higher energy studies with the LAT have been my focus since the beginning. Talk about what's nice about staying above 1 GeV, 10 GeV, 50 GeV. 

GeV TeV connection for 2FHL

Radio GeV for SNR cat (traces same particle population)

The advent of the \lat presents for the first time the capability to spectrally and spatially resolve \gls{snr} at \gev energies.

it is uniquely situated to address these issues

egret was mostly pointed observation instrumented that would sometimes dwell on a spot for a couple of weeks, had a smaller field o view, didn't get as many photons (the LAT saw the entire EGRET sky in some short amount of time)

\snrs as sources of relativistic particles

Despite being the prime energy range to observe the effects of cosmic particle acceleration, the photon \sed{} resulting from these overlapping emission channels are often difficult to spectrally distinguish from one another. \jamie{what's the point of this last sentence here? maybe no need to mention this now, i really just want to motivate GeV energies}

when talking about \egret{}

With its unprecedented sensitivity and angular resolution above 1\gev, the \lat~provides for the first time the opportunity to distinguish SNR-emitted photons from their backgrounds, and  to unambiguously detect and identify dozens of \glspl{snr}. \jamie{maybe this is for the intro/abstract because it's a little vague}

The \lat{} is uniquely situated to address these goals and definitively detect and identify dozens \snrs

snrs as source of Galactic cosmic rays, and thus as drivers of Galactic evolution

\cite{Thomson93} gives the 68\% containment radius as $\theta \leq 5.85^\circ (E_\gamma /100 \mev )^{-0.534}$
\section{I Think I Hate Most of the Section Titles :(}

\section{Maybe None of the Chapters Need Introductions?}

\section{Dissertation Overview}



